
```{r include = FALSE}
source("common.R")
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
library(tidyverse)
library(devtools)
library(DT)
library(vembedr)
library(knitr)
```

```{r links, child="content/links.md"}
```


# Attribution {-}
I have heavily adapted pieces from other lab manuals/handbooks. I will do my best to properly attribute sources. However, I strongly suspect that as this document grows and develops attributions will be harder and harder to keep track of. 

This document leans heavily on other peoples' materials and ideas. I have done my best to document the origin of the materials and ideas. In particular, I have noted those people whose work has been a major contribution as well as those who have additional contributions. You can see specific changes by examining the [edit history on the git repo][commits]

## Major Attributions  {-}

* Jenny Bryan's ([jennybryan.org](https://jennybryan.org)) [STAT 545][stat545]
* [Candice Morey's lab handbook](https://github.com/CCMorey/labHandbook)
* [Jonathan Peelle's lab manual](http://jpeelle.net/peellelab_manual.pdf)
* [Joshua Hartshorne's Language Learning Lab Manual](http://l3atbc.org/L3Manual.pdf)


# License {-#license}

This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-sa/4.0/).

<center>
<i class="fab fa-creative-commons fa-2x"></i><i class="fab fa-creative-commons-by fa-2x"></i><i class="fab fa-creative-commons-sa fa-2x"></i>
</center>

*This information is a human-readable summary of (and not a substitute for) the license.
Please see <https://creativecommons.org/licenses/by-sa/4.0/legalcode> for the full legal text.*

**You are free to:**

- **Share**---copy and redistribute the material in any medium or
  format

- **Remix**---remix, transform, and build upon the material for any
  purpose, even commercially.

The licensor cannot revoke these freedoms as long as you follow the
license terms.

**Under the following terms:**

- **Attribution**---You must give appropriate credit, provide a link
  to the license, and indicate if changes were made. You may do so in
  any reasonable manner, but not in any way that suggests the licensor
  endorses you or your use.
  
- **ShareAlike**---If you remix, transform, or build upon the material, you must distribute your contributions under the same license as the original. 

- **No additional restrictions**---You may not apply legal terms or
  technological measures that legally restrict others from doing
  anything the license permits.

**Notices:**

You do not have to comply with the license for elements of the
material in the public domain or where your use is permitted by an
applicable exception or limitation.

No warranties are given. The license may not give you all of the
permissions necessary for your intended use. For example, other rights
such as publicity, privacy, or moral rights may limit how you use the
material.

```{r include = FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```




# Colophon {-}

These notes was written in [bookdown](http://bookdown.org/) inside [RStudio](http://www.rstudio.com/ide/). The [website][web] is hosted with [github](https://www.github.com), The complete source is available from [github][git].

The book style adapted from designs by [Desirée De Leon](https://desiree.rbind.io/).

This version of the notes was built with:

```{r message = FALSE,error=TRUE, warning = FALSE, echo = FALSE}
# needed because new_session is set to true in _bookdown.yml
all_pkgs <- renv::dependencies(path = "DESCRIPTION") %>% 
  pull(Package) 

session <- devtools::session_info(pkgs = all_pkgs)

session$platform
```

Along with these packages:

```{r message = FALSE,error=TRUE, warning = FALSE, echo = FALSE}
session$packages %>% 
  select(package, loadedversion, date, source) %>% 
  DT::datatable(rownames = FALSE,
                class = 'cell-border stripe',
                filter = list(position = 'top'),
                options = list(pageLength = nrow(session$packages), 
                           autoWidth = TRUE,
                           bInfo = FALSE,
                           paging = FALSE))
```

