
```{r include = FALSE}
source("common.R")
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
library(tidyverse)
library(devtools)
library(DT)
library(vembedr)
library(knitr)
```

```{r links, child="links.md"}
```

# Who R we?

The R Computing Lab houses scientists who conduct biometrically-informed research in R. Our research addresses a mixture of substantive and methodological questions. We're part of the MegaLab with Veronica Cole!

Our substantive work focuses understanding the relationships between socioeconomic status, health & well-being, and individual differences (personality, intelligence). Our methodological work focuses on developing and improving biometrically-informed designs, such as behavior genetic and discordant kin models. 

Students in the laboratory work on projects covering a wide range of topics including inter-generational consequences of divorce, vaccination willingness, R package development.


Members are listed by seniority (in the order they joined the lab).

## Investigators

### Principal Investigator

* S. Mason Garrison

### Affiliated Principal Investigator
* Veronica Cole


## Current Students

### Graduate Students
#### Primary Lab

* Yoo Ri Hwang
* Xuanyu Lyu


#### Affiliated (Primary Lab)

* Emma Sims (Jayawickreme)
* Jonathan Trattner

### Undergraduate Students
* Kennon Later
* Hannah Robertson
* out of date


### Sidekicks
* Tukey
* Archie & Annie


## Prior Members

#### Graduate Students
##### Affiliated (Primary Lab)

* Lindley Slipetz (Cole)

### Undergraduate Students
* Nora Clancy
* Sherry Mao
* Jonathan Trattner


# Lab Philosophy

## You won't know everything

Ask questions! It is ok to not know something. I don't know everything. It is the sign of a good scholar to ask questions and it is the sign of a confident scholar to be willing to say that they don't know.

## Work-Life Balance

We value work-life balance.
