
```{r include = FALSE}
source("common.R")
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
library(tidyverse)
library(devtools)
library(DT)
library(vembedr)
library(knitr)
```

```{r links, child="links.md"}
```

# Who R we? {-}

Members are listed by seniority (in the order they joined the lab).

## Investigators
----------
### Principal Investigator

* S. Mason Garrison

### Affiliated Principal Investigator
* Veronica Cole

----------
## Current Students
----------
### Graduate Students
#### Primary Lab
* Yoo Ri Hwang
* Open Position for Fall 2021


#### Affiliated (Primary Lab)

* [Emma Sims] (Jayawickreme)


### Undergraduate Students
* Kennon Later
* Jonathan Trattner
* Sherry Mao
* Hannah Robertson
* 




### Sidekicks
* Tukey
* Archie & Annie

----------
## Prior Members
----------
#### Graduate Students
##### Affiliated (Primary Lab)
* Lindley Slipetz (Cole)

### Undergraduate Students
* Nora Clancy

# What R we doing? {-}

## Active Projects

The R Computing Lab also has a github.... https://github.com/R-Computing-Lab

For the most current list... navigate to the "[Active Projects](https://osf.io/5syrj/)" folder within OSF storage below. 
 * Discordant Kinship R Package
 * Divorce and Depression
 * Vaccination Willingness and SES
 * Depression and Delinquency
