# (PART) Introductions {-}

```{r include = FALSE}
source("common.R")
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
library(tidyverse)
library(devtools)
library(DT)
library(vembedr)
library(knitr)
```


# Who R we?

```{r child="content/info_rlab.md"}
```

Our substantive work focuses understanding the relationships between socioeconomic status, health & well-being, and individual differences (personality, intelligence). Our methodological work focuses on developing and improving biometrically-informed designs, such as behavior genetic and discordant kin models. Much of the research in my lab is student-driven, so the specific content questions will meander within that broad topic. :)

Students in the laboratory work on projects covering a wide range of topics, including inter-generational consequences of divorce, vaccination willingness, R package development.

```{r child="content/info_values.md"}
```


Members are listed by seniority (in the order they joined the lab).

## Investigators

### Principal Investigator

* S. Mason Garrison

### Affiliated Principal Investigator
* Veronica Cole


## Current Students

### Graduate Students
#### Primary Lab

* Xuanyu Lyu


#### Affiliated (Primary Lab)
* Qilin Zhang (Fleeson)
* Jonathan Trattner (Kishida)
* Emma Sims (Jayawickreme)
* Rachel Good (Furr)

### Undergraduate Students

#### Honors
* Mary King

#### Volunteer

* Laura McKinzie
* Emma Webster
* Mary King
* Holland Tyson
* Sarah Haga
* Lena Arnsten
* Reese Fortier

### Sidekicks
* Tukey
* Archie & Annie


## Prior Members

#### Graduate Students
* Yoo Ri Hwang

##### Affiliated (Primary Lab)

* Lindley Slipetz (Cole)

### Undergraduate Students

#### Honors Students
* Rachel Good

#### Volunteers
* Mark Rivilis
* Hannah Robertson
* Morgan Milhollen
* Sarah Thompson
* Rachel Good
* Nora Clancy
* Sherry Mao
* Kennon Later
* Jonathan Trattner


