
```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
ds4p_urls <- read.csv("./data/ds4p_urls.csv")
```

```{r links, child="links.md"}
```

# (PART) Being in the lab {-}



# Being in the lab

Ok, so what does it mean to be part of the R computing lab? Well, let's start with my goals and expectations.

```{r child="values.md"}
```

This handbook is a first point of reference for current lab members as we strive to achieve these goals, and serves as a general introduction for prospective members. 


## Everyone

Generally, don't be an asshole. 

### You won't know everything

Ask questions! It is ok to not know something. I don't know everything. It is the sign of a good scholar to ask questions and it is the sign of a confident scholar to be willing to say that they don't know.

### Work-Life Balance

We value work-life balance.


## Mason
You can expect me to:

- Have a vision of where the lab is going.
- Care about your happiness, health, and well-being.
- Obtain the funding to support the science and the people in the lab.
- Track down interesting sources of data.
- Support you in your career development (regardless of whether you plan to stay in research), including: 
    - writing letters of recommendation,
    - introductions to other scientists, 
    - subsidizing conference travel, and 
    - promoting your work as often and as shamelessly as possible.

- Support you in your personal growth, including (but not limited to):
    - giving you flexibility in working hours and environment, and 
    - encouraging you to do things other than science.

- Treat you to coffee and keep the snack drawer filled.

- Make the time to meet with you regularly, read through your manuscripts, and talk about science.



## Graduate Students

I expect graduate students to:
- Know the literature related to their topic.
- Seek out and apply for fellowships and awards (including travel awards, etc.).
- Realize there are (extraordinarily rare) times for pulling all nighters, and times for leaving early to go to the park and enjoy the sunshine.

By the time you're done, you will have to know how to do statistics and plots in R, share your work with me using Rmarkdown, use mplus for latent variable modeling and use github for version control analyses.

The learning curve can be a little steep on these but it's well worth it. (If these learning outcomes aren't compatible with your goals or interests, my lab is probably not a good fit for you!)




## Undergraduate Students

I expect undergraduates to be utterly reliable and willing to help with whatever projects need it. At a bare minimum, reliability includes showing up on time and making sure that all of your work is accurate (double-check everything). If you find yourself without a specific project:

- Ask around to see if you can help with anything.
- Look on the wiki under "Essential lab skills" and spend some time learning something new.
- Look on the giant lab todo list for either a wiki page that needs creating/updating, or other miscellaneous lab tasks that need to be done.

There is enough to do that you should not be bored!

Your first semester in the lab is an opportunity to see whether continuing in the lab is a good fit; after your first semester we will meet and discuss whether you will continue.



### Honors Students

### Independent study




## University Policies
### Employee guidelines
### Sexual harassment


