# (PART) Being in the lab {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
ds4p_urls <- read.csv("./data/ds4p_urls.csv")
```

```{r links, child="links.md"}
```



# Being in the lab
## Everyone
### Big Picture
### Small Picture

## Mason
You can expect me to:
- Have a vision of where the lab is going.
- Care about your happiness.
- Obtain the funding to support the science and the people in the lab.
- Track down interesting sources of data.
- Support you in your career development (regardless of whether you plan to stay in research), including: 
    - writing letters of recommendation,
    - introductions to other scientists, 
    - subsidizing conference travel, and 
    - promoting your work as often and as shamelessly as possible.

- Support you in your personal growth, including (but not limited to):
    - giving you flexibility in working hours and environment, and 
    - encouraging you to do things other than science.

- Treat you to coffee and keep the snack drawer filled.

- Make the time to meet with you regularly, read through your manuscripts, and talk about science.



## Graduate Students

I expect graduate students to:
- Know the literature related to their topic like the back of their hand.
- Seek out and apply for fellowships and awards (including travel awards, etc.).
- Realize there are (extraordinarily rare) times for pulling all nighters, and times for leaving early to go to the park and enjoy the sunshine.

By the time you're done, you will have to know how to do statistics and plots in R, share your work with me using Rmarkdown, use mplus for latent variable modeling and use github and osf for version control analyses.

The learning curve can be a little steep on these but it's well worth it. (If these learning outcomes aren't compatible with your goals or interests, my lab is probably not a good fit for you!)


### General Timeline

The timeline below is intended to help you structure your time during the WFU graduate program-- to stay on track with: 
- non-coursework program requirements, 
- professional development opportunities (conferences), and 
- PhD applications, if you plan to apply. 

It likely not comprehensive for your unique situation, and it is expected that you will personalize it. 

Sources of Adaptation ([The AMAZING Shannon Brady](https://psychology.wfu.edu/about-the-department/faculty-and-staff/shannon-brady/))

#### Year 1

August

- Match with Advisor
- Consider Submitting to SSSP


September

- Acclimate! Get lab key
- Discuss interests and goals with advisor; personalize timeline


October

- Read relevant literature
- Review Grad Handbook sections for Year 1 
- Begin to develop First Year Project (FYP)
- Consider attending SSSP 


November

- Read relevant literature
- Present FYP to peers; get feedback


December

- Read relevant literature
- Refine plan for FYP
- If needed: Secure IRB approval for FYP 
    - (In my lab needing IRB approval is rare)


January

- Begin data collection OR begin data cleaning/analysis


February

- Collect data and/or clean and analyze data


March

- Collect data and/or clean and analyze data
- Discuss initial ideas for MAP w/ advisor
- Find template for FYP poster; 
    -  discuss w/ advisor
- Consider submitting FYP to BGA

April

- Create and revise FYP poster
- Present FYP Poster


May

- Review Grad Handbook sections for Year 2 
- Discuss initial ideas for MAP w/ advisor
- Generate initial list of PhD topics/advisors; 
    - discuss w/ mentors 
- Consider submitting to a conference (like SPSP)



June

- Identify articles to be "mentor texts"
- Draft Methods section of MAP; get feedback
- Read papers by prospective advisors

July

- Draft Results section of MAP; get feedback
- Read papers by prospective advisors
- Create/update CV
- Consider submitting to SPSP


#### Year 2
August
- Review Grad Handbook expectations for MAP
- Create complete outline of MAP
    - get feedback
- Submit MAP outline and annotated biblio
- Refine list of PhD advisors; 
    - reach out
- Write crappy first draft of SOP
- Consider submitting to SSSP


September
- Schedule MAP feedback mtg
- Send MAP to all committee members
- Contact letter writers
- Discuss SOP with mentors/peers/friends

October
- Have MAP feedback mtg
    - If needed: revise MAP
- Review Grad Handbook expectations for thesis
- Finalize thesis idea
- Review and revise SOP;
- draft any other materials needed for applications
- Send materials to letter writers
- Consider attending SSSP


November

December

January

February

March

April

May

June

July

### Useful Websites

https://graduate.wfu.edu/graduation-requirement-checklist-reynolda-campus/

## Undergraduate Students

I expect undergraduates to be utterly reliable and willing to help with whatever projects need it. At a bare minimum, reliability includes showing up on time and making sure that all of your work is accurate (double-check everything). If you find yourself without a specific project:

- Ask around to see if you can help with anything.
- Look on the wiki under "Essential lab skills" and spend some time learning something new.
- Look on the giant lab todo list for either a wiki page that needs creating/updating, or other miscellaneous lab tasks that need to be done.

There is enough to do that you should not be bored!

Your first semester in the lab is an opportunity to see whether continuing in the lab is a good fit; after your first semester we will meet and discuss whether you will continue.



### Honors Students

### Independent study




## University Policies
### Employee guidelines
### Sexual harassment



# Communication 
## Communication within the lab
### My doors

###  Lab Meetings

Lab members participate in both regular and ad hoc meetings. These meetings may involve everyone or just subgroups. If you have been asked to participate in a meeting, it is because you are a vital part of that project group. If you cannot attend, you should tell the group leader in advance. Remember, however, that the group may no longer be able to carry out the intended work without your presence, so skip meetings sparingly. 

If you do not appear at a meeting as expected and have not informed anyone in advance, it will be assumed that you have been abducted by aliens, and a search-and-rescue mission will be organized. I will draw [inspiration](https://www.nbcnews.com/news/world/how-swedish-professor-helped-rescue-grad-student-isis-controlled-iraq-n947866) from Prof. Charlotta Turner of Lund University.

All meetings begin and end on time, if not earlier. Don't be afraid to remind me of this if/when I am the offending party. It is important that we all respect each other's time.




### Wiki

The lab wiki is our shared collection of knowledge about how to get things done in the lab. The lab handbook you are reading now is "top down", in that I am writing the whole thing myself. By contrast the wiki is a shared resource to which everyone can—and should—contribute. A good rule of thumb is that if you need to figure out how to do something, someone else in the lab may someday need to do the same thing. Whenever possible please document what you figure out on the wiki, including updating old sections which may no longer be relevant. Please encourage each other (and those working with you) to do the same! (And me, please remind me!)

Sources of Adaptation ([2])

### Email

### Calendars


## Communication outside the lab
### Manuscripts
### Abstracts
#### Talks
#### Posters


## Conferences

Conferences are excellent opportunities to present your research, make connections, and learn about new research and methods from others. If possible, I recommend attending two or more conferences while you are a graduate student at Wake Forest and presenting your research at one or more of the conferences you attend.    

