
```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets

```

```{r links, child="links.md"}
```



# Science
## Big picture science
### Scientific integrity


You have a responsibility to me, the institutions that support our work, and the broader scientific community to uphold the highest standards of scientific accuracy and integrity. By being in the lab you agree to adhere to professional ethical standards. There is never an excuse for fabricating or misrepresenting data. If you have any questions, or in the unlikely event that you have concerns about a research practice you have seen in the lab, please talk to me immediately. It is also important that you prioritize the accuracy of your work while in the lab. Unintentional errors due to inattentiveness or rushing can be extremely damaging and produce results that turn out to be incorrect. Although there is always a pressure for a high quantity of research, it is critical that everything we do is of the highest quality. Please double-check your work frequently. In many cases multiple people will double-check a data set to ensure no mistakes have crept in along the way.


### Open, accurate, and reproducible science
#### Open science
#### Accurate science

## Practical science

### Writing

#### Abstracts

```{r, echo=FALSE}
include_tweet("https://twitter.com/DrasmaJabeen1/status/1459448488048140294")

```
### Computers and data
### Authorship

My general philosophy is to be generous and provide ample opportunity for members of the lab to earn authorship. Authorship on an academic work is a ["public acknowledgment of scientific or professional contribution"](https://www.apa.org/science/leadership/students/authorship-paper). Although the criteria for authorship differ slightly across fields, the general question asked is whether this individual made a meaningful contribution to the work. I tend to ask myself had this potential author not been involved in the project, would the final product differed substantially? If the answer to that counter-factual is yes, then I believe that person has earned authorship.

#### Order of Authors

In psychology, the order of authors reflects their relative contribution. Other fields have different conventions, such as economics tends to alphabetize authors. However, psychology and other lab-based fields don't merely rank authors. Instead the authorship order resembles a 'U' where first and last authors indicate the most substantial contributions and authors in the middle reflect relatively smaller contributions. Practically speaking, this ordering means that I (Mason) will probably be last author, and any project that you, dear reader, lead are first author.
