# (PART) Resources {-}

```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets

```


# Academic Career Resources

This project gathers together all the resources I've gathered throughout my career. The collections are currently divided into Graduate School Applications and Academic Job Search. Clearly, there's much to add in between those two stages, such as graduate school, fellowships, and the like. 



# Useful Articles

 - [Edyburn, Dave (August 21, 2020). [An Onboarding Guide for Postdoctoral Researchers. Inside Higher Ed](https://www.insidehighered.com/advice/2020/08/21/advice-postdocs-during-start-phase-their-appointments-opinion)
 
 
# Graduate Application Resources
https://osf.io/jvdx7/wiki/home/

## Motivation

Here are an incomplete collection of resources for students interested in applying to graduate school in psychology. I've included my application materials that I used for the PhD program I enrolled in. NOTE: I really feel that I was accepted in spite of my application essay. However, in the spirit of transparency, I've included it anyway.




## General Advice



### Psychology
- [Mitch Prinstein](http://mitch.web.unc.edu/info-for-phd-applicants/)'s collection of info for PHD applicants including:
    - [Mitch's Uncensored Advice for Applying to Graduate School in Clinical Psychology](http://mitch.web.unc.edu/files/2017/02/MitchGradSchoolAdvice.pdf) 
    - [Tips on Applying to Graduate School](http://mitch.web.unc.edu/files/2013/10/TipsForApplyingToGradSchool.pdf) by Sophie Choukas-Bradley
    - [Before You Apply](http://mitch.web.unc.edu/files/2013/10/BeforeYouApply.pdf) by Casey Calhoun

- [Bill Revelle](https://www.personality-project.org)'s [Website has a collection of info](https://www.personality-project.org/org.html#howtoapply) 

### Should you go?

- The Economist on [Why doing a PhD is often a waste of time](https://medium.economist.com/why-doing-a-phd-is-often-a-waste-of-time-349206f9addb)
- Richard Z on [Why Would You Want to Do a PhD?: Student perspectives on the value of a graduate degree](https://gradadmissions.mit.edu/blog/why-would-you-want-do-phd)


## Application

```{r, echo=FALSE}
if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets

include_tweet("https://twitter.com/crisbanksleite/status/1453753460357218306")
```


- [Appleby, D. C., & Appleby, K. M. (2006). Kisses of death in the graduate school application process. Teaching of Psychology, 33(1), 19-24.](https://psychology.unl.edu/psichi/Graduate_School_Application_Kisses_of_Death.pdf)

- [Philip Guo's](http://www.pgbovine.net/index.html) [A Five-Minute Guide to Ph.D. Program Applications](http://www.pgbovine.net/PhD-application-tips.htm)

## Programs
### What area of psychology?

- Wikipedia's Lists 
    - [Subfields of psychology](https://en.wikipedia.org/wiki/Subfields_of_psychology), 
    - [Psychology Disciplines](https://en.wikipedia.org/wiki/List_of_psychology_disciplines)

### Lists

#### Funded Terminal Master's Programs (Incomplete List)

- [College of William and Mary](https://www.wm.edu/as/psych-sciences/gradprogram/financial-support/index.php)
- [Villanova University](https://www1.villanova.edu/villanova/artsci/psychology/AcademicPrograms/graduate/current/assistantships.html)
- [Wake Forest University](http://psychology.wfu.edu/graduate-program/graduate-financial-aid-2/)



#### Subfield

- Clinical Psychology
    - [American Psychological Association](https://www.apa.org/index)'s [List of APA-Accredited Programs](https://www.apa.org/ed/accreditation/programs/)


- Individual Differences (Personality, Intelligence, etc)
    - [Bill Revelle](https://www.personality-project.org)'s List of [Graduate Departments of Psychology with Personality Programs](https://www.personality-project.org/org.html#gradpsych)


- Quantitative Psychology
    - [List of schools for quantitative psychology](https://en.wikipedia.org/wiki/List_of_schools_for_quantitative_psychology)

- Social Psychology
    - [Social Psychology Network Ranked List](https://www.socialpsychology.org/gsocial.htm)
    - [SPSP's Social and Personality Graduate Program Directory](http://spsp.org/resources/student/grad-directory)

## Subreddits
- [/r/Gradadmissions](https://www.reddit.com/r/gradadmissions/)
- [/r/GradSchool](https://www.reddit.com/r/GradSchool/)
- [/r/AskAcademia](https://www.reddit.com/r/AskAcademia)

# Graduate Student Life

- [Graduate School Survival Guide](http://www.cs.unc.edu/~azuma/hitch4.html)
- [PhD Comics](http://phdcomics.com/)



# Quantitative Methods Psych Jobs 
<!-- https://osf.io/nhmuv/wiki/home/?edit&view&menu -->
## Motivation

I had a tough time finding examples of job materials for quantitatively-inclined candidates. Here are representative examples from my own materials. Hopefully, they'll be able to help inspire your own materials. In addition, I've added some of the other resources and information that I found helpful. Although this collection has focused on academic jobs, I also considered industry jobs in my search.


## Resources
This is an incomplete list. Suggestions are very much encouraged.

### General Advice

- The Professor Is In: [Blog](http://theprofessorisin.com/) and [Book](https://smile.amazon.com/gp/product/0553419420)

- American Psychological Association [APA Career Resources](https://www.apa.org/careers/resources/academic/)

### Materials

#### Cover letter
- [How To Write Academic Job Cover Letters from The Professor Is In](https://theprofessorisin.com/category/how-to-write-academic-job-cover-letters/)

#### Teaching Statements
- [Vanderbilt Center for Teaching on Teaching Statements]( https://cft.vanderbilt.edu/guides-sub-pages/teaching-statements/)
- [Writing a Teaching Philosophy Statement by Helen G. Grundman](http://www.ams.org/notices/200611/comm-grundman.pdf)
- [University of Arizona on Writing Diversity Statements](https://postdoc.arizona.edu/content/writing-diversity-statements)

#### Research Statements

#### Diversity Statements
- [The Effective Diversity Statement from InsideHigherEd](https://www.insidehighered.com/advice/2016/06/10/how-write-effective-diversity-statement-essay)
- [Beck, S. L., (2018). Developing and writing a diversity statement. Vanderbilt University Center for Teaching](https://cft.vanderbilt.edu/guides-sub-pages/developing-and-writing-a-diversity-statement/)

#### Example Materials

- UCSF [Samples for Academic Positions](https://career.ucsf.edu/grad-students-postdocs/career-planning/academic-jobs/applying/academic-samples)
- [Plasticity in Neurodevelopment Lab](https://www.plasticityinneurodevelopmentlab.com/for-academics)
- Mine


## Finding Jobs

### Academic
- [APA PsychCareers](https://www.psyccareers.com/search)
- [APS Employment Network](https://jobs.psychologicalscience.org/)
- [HigherEd Jobs](https://www.higheredjobs.com/faculty/search.cfm?JobCat=91)
- [Psych Jobs Wiki](http://psychjobsearch.wikidot.com/)
- [SMEP Job Postings](https://smep.org/resources/positions-available)
- [Society for Math Psych](http://www.mathpsych.org/index.php?option=com_content&view=category&layout=blog&id=34&Itemid=62)
- [SPSP](https://my.spsp.org/Careers/Job-Search)
- [Times Higher Education](https://www.timeshighereducation.com/unijobs/en-us/listings/psychology/)

### Industry
Most data-savvy companies have a careers page. I've included some of those pages here of companies I applied to, were recruited by, or would be interested in working for. There are also job boards, which companies post positions on. There's some overlap, but not 100%.

#### Specific Companies
- [23andMe](https://www.23andme.com/careers/)
- [ACT](https://careers-act.icims.com/jobs/)
- [Amazon](https://www.amazon.jobs/en/job_categories/data-science)
- [Ancestry](https://careers.ancestry.com/us/en)
- [ETS](https://www.ets.org/careers)
- [Facebook](https://www.facebook.com/careers/jobs)
- [Google](https://careers.google.com/)
- [Houghton Mifflin Harcourt](https://careers.hmhco.com/key/educational-measurement-jobs.html)
- [ITHAKA (JSTOR, Ithaka S+R, Portico)](https://www.ithaka.org/career-opportunities)
- [New York Times](https://www.nytco.com/careers/)
- [Pearson](https://pearson.jobs/)
- [Pew Research Center](https://jobs-prc.icims.com/jobs/)
- [RAND](https://www.rand.org/jobs.html)
- [SSRS](https://ssrs.com/careers/)
- [W. W. Norton & Company](https://wwnorton.com/careers/current-openings)

#### Job Postings
- [Glassdoor](https://www.glassdoor.com)
- [Indeed](https://www.indeed.com/)
- [USA Jobs (US Government Jobs)](https://www.usajobs.gov/)


## Data / Research

- Bureau of Labor Statistics on [STEM crisis or STEM surplus? Yes and yes](https://www.bls.gov/opub/mlr/2015/article/stem-crisis-or-stem-surplus-yes-and-yes.htm)
- [What are the chances of becoming a Psychology Professor?](http://geekpsychologist.com/what-are-the-chances-of-becoming-a-psychology-professor/stem-surplus-yes-and-yes.htm)
    -[(archived link)](http://webcache.googleusercontent.com/search?q=cache:M-P4L1Xj8XoJ:geekpsychologist.com/what-are-the-chances-of-becoming-a-psychology-professor/&hl=en&gl=us&strip=0&vwsrc=0)
- [Boysen, G. A., Morton, J., & Nieves, T. (2019). Kisses of Death in the Psychology Faculty Hiring Process. Teaching of Psychology](https://journals.sagepub.com/doi/abs/10.1177/0098628319853942)
- [Boysen, G. A., Jones, C., Kaltwasser, R., & Thompson, E. (2018). Keys to a successful job talk: Perceptions of psychology faculty. Teaching of Psychology, 45(3), 270-277.](https://journals.sagepub.com/doi/full/10.1177/0098628318779277)
- [Pennycook, G. & Thompson, V. A. (2018). An analysis of the Canadian cognitive psychology job market (2006-2016). Canadian Journal of Experimental Psychology, 72, 71-80.](https://psyarxiv.com/mxa35)
- Washington Post on [The academic job market is a nightmare](https://www.washingtonpost.com/outlook/2019/04/15/job-market-academics-is-nightmare-heres-one-way-fix-it/)
- Jeremy Yoder on [I Found a Tenure-Track Job. Here's What it Took](https://chroniclevitae.com/news/1775-i-found-a-tenure-track-job-here-s-what-it-took)
