```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets

```

# Graduation Admissions Advice

## Motivation

Here are an incomplete collection of resources for students interested in applying to graduate school in psychology. I've included my application materials that I used for the PhD program I enrolled in. NOTE: I really feel that I was accepted in spite of my application essay. However, in the spirit of transparency, I've included it anyway.



## General Advice

### Psychology

- [Mitch Prinstein](http://mitch.web.unc.edu/info-for-phd-applicants/)'s collection of info for PHD applicants including:
    - [Mitch's Uncensored Advice for Applying to Graduate School in Clinical Psychology](http://mitch.web.unc.edu/files/2017/02/MitchGradSchoolAdvice.pdf) 
    - [Tips on Applying to Graduate School](http://mitch.web.unc.edu/files/2013/10/TipsForApplyingToGradSchool.pdf) by Sophie Choukas-Bradley
    - [Before You Apply](http://mitch.web.unc.edu/files/2013/10/BeforeYouApply.pdf) by Casey Calhoun

- [Bill Revelle](https://www.personality-project.org)'s [Website has a collection of info](https://www.personality-project.org/org.html#howtoapply) 

### Should you go?

- The Economist on [Why doing a PhD is often a waste of time](https://medium.economist.com/why-doing-a-phd-is-often-a-waste-of-time-349206f9addb)
- Richard Z on [Why Would You Want to Do a PhD?: Student perspectives on the value of a graduate degree](https://gradadmissions.mit.edu/blog/why-would-you-want-do-phd)


## Application

```{r, echo=FALSE}

include_tweet("https://twitter.com/crisbanksleite/status/1453753460357218306")
```


- [Appleby, D. C., & Appleby, K. M. (2006). Kisses of death in the graduate school application process. Teaching of Psychology, 33(1), 19-24.](https://psychology.unl.edu/psichi/Graduate_School_Application_Kisses_of_Death.pdf)

- [Philip Guo's](http://www.pgbovine.net/index.html) [A Five-Minute Guide to Ph.D. Program Applications](http://www.pgbovine.net/PhD-application-tips.htm)

## Programs
### What area of psychology?

- Wikipedia's Lists 
    - [Subfields of psychology](https://en.wikipedia.org/wiki/Subfields_of_psychology), 
    - [Psychology Disciplines](https://en.wikipedia.org/wiki/List_of_psychology_disciplines)

### Lists

#### Funded Terminal Master's Programs (Incomplete List)

- [College of William and Mary](https://www.wm.edu/as/psych-sciences/gradprogram/financial-support/index.php)
- [Villanova University](https://www1.villanova.edu/villanova/artsci/psychology/AcademicPrograms/graduate/current/assistantships.html)
- [Wake Forest University](http://psychology.wfu.edu/graduate-program/graduate-financial-aid-2/)


### Subfield

- Clinical Psychology
    - [American Psychological Association](https://www.apa.org/index)'s [List of APA-Accredited Programs](https://www.apa.org/ed/accreditation/programs/)


- Individual Differences (Personality, Intelligence, etc)
    - [Bill Revelle](https://www.personality-project.org)'s List of [Graduate Departments of Psychology with Personality Programs](https://www.personality-project.org/org.html#gradpsych)


- Quantitative Psychology
    - [List of schools for quantitative psychology](https://en.wikipedia.org/wiki/List_of_schools_for_quantitative_psychology)

- Social Psychology
    - [Social Psychology Network Ranked List](https://www.socialpsychology.org/gsocial.htm)
    - [SPSP's Social and Personality Graduate Program Directory](http://spsp.org/resources/student/grad-directory)

## Subreddits
- [/r/Gradadmissions](https://www.reddit.com/r/gradadmissions/)
- [/r/GradSchool](https://www.reddit.com/r/GradSchool/)
- [/r/AskAcademia](https://www.reddit.com/r/AskAcademia)
