# (PART) Useful Things {-}

```{r include = FALSE}
source("common.R")
# install.packages("devtools")
if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets
```

```{r links, child="content/links.md"}
```

# Software

This wikipage contains the collective lab knowledge about software and coding. Sections are kind of organized logically.



## R & Rstudio

There are tons more stuff about R in my [Data Science for Psychologists class.](https://datascience4psych.github.io/DataScience4Psych/)



### Base R

### R studio

### R Code

This subsection contains R code that I have googled more than once.

#### How do I export a dataframe?

Description: export a dataframe to specific data type?

Source: [Quick-R](https://www.statmethods.net/input/exportingdata.html)


 - dat

> write.table(mydata, "mydata.dat", sep="\t")
    
 - csv
 
> write.csv(mydata,"mydata.csv", row.names = FALSE)



#### How do I merge a list of dataframes?

Description: Merges list of dataframes into a single dataframe

Source: [stackoverflow]( https://stackoverflow.com/questions/2851327/convert-a-list-of-data-frames-into-one-data-frame/38509685)


> bind_rows(list_of_dataframes, .id = "column_label")

Note: .id = "column_label" adds the unique row names based on the list element names


#### How do I produce all combinations of list elements?

Description: produce all combinations of list elements

Source: [rdrr.io](https://rdrr.io/r/base/expand.grid.html)

```{r}
require(utils)

expand.grid(height = seq(60, 80, 5), 
            weight = seq(100, 300, 50), 
            type = c("Cat","Dog"))
```

#### How to remove scientific notation?

Description: Stop R from printing tiny decimals as strings

Source: [stackoverflow](https://stackoverflow.com/questions/5352099/how-to-disable-scientific-notation)

```{r}

options(scipen = 999)

```


# Browsers/Internet

## Google
This section contains google-related code that I have googled more than once

### Search Operators
[Source]( https://ahrefs.com/blog/google-advanced-search-operators/)


#### cache

Description: Returns the most recent cached version of a web page 
 
> cache:


#### filetype

Description: Restrict results to those of a certain filetype. e.g., PDF, DOCX, TXT, PPT, etc.

> filetype:
 
#### site    
Description: Limit results to those from a specific website.

> site:
    
#### related
Description: Find sites related to a given domain.

> related:


#### intitle
Description: Find pages with a certain word (or words) in the title. 

> intitle:


#### Proximity
Description: Proximity search. Find pages containing two words or phrases within X words of each other.

> AROUND(X)



## Javascript Bookmarklets

A bookmarklet is a bookmark stored in a web browser that contains JavaScript commands that add new features to the browser. 
(Source: [Wikipedia](https://en.wikipedia.org/wiki/Bookmarklet))

### WFU Related

Description: Redirects you to the WFU proxied version of the website

> javascript:void(location.href="http://go.libproxy.wakehealth.edu/login?url="+location.href)
    
Source: Mason

### Google Related



#### Switch google accounts


Description: If you have multiple google accounts, you can add "?authuser=1" to switch to your 2nd account.

> javascript:window.location.href=window.location.href+'?authuser=1'

Source: Mason

#### Google Cache 

Description: Text-only version of google Cache


> javascript:(function(){var loc=window.location;if (window.location.protocol != "https:"){loc=window.location.toString().replace(/^http:\/\//,'http://webcache.googleusercontent.com/search?q=cache:');}else{loc=window.location.toString().replace(/^https:\/\//,'https://webcache.googleusercontent.com/search?q=cache:');}window.location.replace(loc + '&num=1&strip=1&vwsrc=0')})()

Source: [Online Techtips](https://www.online-tech-tips.com/cool-websites/the-12-best-bookmarklets-every-browser-should-have/)

### Google Translate 

Description: Autodetect language and translate into English


> javascript:var t=((window.getSelection&&window.getSelection())||(document.getSelection&&document.getSelection())||(document.selection &&document.selection.createRange&&document.selection.createRange().text));var e=(document.charset||document.characterSet);if(t!=''){location.href='http://translate.google.com/translate_t?text=' t '&hl=en&langpair=auto|en&tbb=1&ie=' e;}else{location.href='http://translate.google.com/translate?u=' escape(location.href) '&hl=en&langpair=auto|en&tbb=1&ie=' e;};

Source: [Online Techtips](https://www.online-tech-tips.com/cool-websites/the-12-best-bookmarklets-every-browser-should-have/)

### Not Otherwise Specified

#### Waybackmachine

Description: "If the webpage you're wanting to read is no longer available, is throwing an error, or the website as a whole has been taken down, you might still have luck finding it on Wayback Machine." 


> javascript:location.href='https://web.archive.org/web/*/'+location.href

Source: [Online Techtips](https://www.online-tech-tips.com/cool-websites/the-12-best-bookmarklets-every-browser-should-have/)





## Userscripts

What are user scripts?

User scripts put you in control of your browsing experience. Once installed, they automatically make the sites you visit better by adding features, making them easier to use, or taking out the annoying bits. The user scripts on Greasy Fork were written by other users and posted to share with the world. They're free to install and easy to use. 

(Source: [GreasyFork](https://greasyfork.org/en/help/installing-user-scripts))


<!--
# Template

## Name

Description: 

> CODE

Note: Additional comments

Source: [URL](https://google.com)

-->
