```{r include = FALSE}
source("common.R")

# install.packages("devtools")

if (!require("tweetrmd"))  devtools::install_github("gadenbuie/tweetrmd")
library(tweetrmd) #... embedding tweets

```

# Graduate School Admissions Advice

## Motivation

Here are an incomplete collection of resources for students interested in applying to graduate school in psychology. I've included my application materials that I used for the PhD program I enrolled in. NOTE: I really feel that I was accepted in spite of my application essay. However, in the spirit of transparency, I've included it anyway.



## General Advice


### Should you go?

- The Economist on [Why doing a PhD is often a waste of time](https://medium.economist.com/why-doing-a-phd-is-often-a-waste-of-time-349206f9addb)
- Richard Z on [Why Would You Want to Do a PhD?: Student perspectives on the value of a graduate degree](https://gradadmissions.mit.edu/blog/why-would-you-want-do-phd)

```{r, echo=FALSE}
"https://twitter.com/jaxwendy/status/1492553462302707714" %>%
include_tweet()
```


## Application

- [Appleby, D. C., & Appleby, K. M. (2006). Kisses of death in the graduate school application process. Teaching of Psychology, 33(1), 19-24.](https://psychology.unl.edu/psichi/Graduate_School_Application_Kisses_of_Death.pdf)

- [Philip Guo's](http://www.pgbovine.net/index.html) [A Five-Minute Guide to Ph.D. Program Applications](http://www.pgbovine.net/PhD-application-tips.htm)


### Personal Statements

```{r, echo=FALSE}
include_tweet("https://twitter.com/cblatts/status/1593606505340801024")
```



### Resumes and CVs

```{r, echo=FALSE}
embed_url("https://youtu.be/42ifhBbyu8A") %>%
  use_align("center")
```


### Recommendation Letters

```{r, echo=FALSE}
try(include_tweet("https://twitter.com/DrBKelleher/status/1455202559988273155"))
```

```{r, echo=FALSE}
embed_url("https://www.youtube.com/watch?v=PJZwQZsoqE0") %>%
  use_align("center")
```

### Contacting Professors

```{r, echo=FALSE}

try(include_tweet("https://twitter.com/crisbanksleite/status/1453753435594047494"))

try(include_tweet("https://twitter.com/crisbanksleite/status/1453753463494610952"))
```

### My Materials

I've included my materials for my application to quantitative psychology graduate programs. You can find them in the [source code for the handbook](https://github.com/R-Computing-Lab/handbook/tree/main/admin/masonmaterials/gradapps). Specifically, here is my CV when I applied (file: [docx](https://github.com/R-Computing-Lab/handbook/blob/main/admin/masonmaterials/gradapps/SMGarrisonCVNOV.docx); [pdf](https://github.com/R-Computing-Lab/handbook/blob/main/admin/masonmaterials/gradapps/SMGarrisonCVNOV.pdf));  and statement of purpose (file: [docx](https://github.com/R-Computing-Lab/handbook/blob/main/admin/masonmaterials/gradapps/VanderbiltStatementofPurpose.docx); [pdf](https://github.com/R-Computing-Lab/handbook/blob/main/admin/masonmaterials/gradapps/VanderbiltStatementofPurpose.pdf)).

## Interviews

```{r, echo=FALSE}

try(include_tweet("https://twitter.com/julie_cristello/status/1466047527518679043"))
```

This collection of questions comes from [this reddit post]( https://www.reddit.com/r/gradadmissions/comments/rxizvp/master_list_of_interview_questions/)

### Motivations

- What motivated you to apply to grad school?
- Why do you feel prepared to start graduate school?
- What areas of research interest you?
- Why do you want to pursue a PhD in your area of interest?
- Do you have any reservations/worries about entering a PhD program?
- What are you looking to gain from your graduate school experience?
- Why do you need a PhD to achieve your career goal?
- Where do you see your field going in the next 5-10 years?
- Where do you see yourself in 15 years?
- What is unique about you that gives you a competitive edge over other applicants?

### The Program/Institution

- Why are you specifically drawn to this program?
- Why do you think this program would be a good fit for you?
- What specific resources does this institution offer to enhance your scientific trajectory?
- How do you think your interests will fit in with the program?
- What do you think you will contribute to the program?
- Which faculty members’ work particularly interests you and why?
- Have you established a relationship with one or more faculty members within the program?
- What interests you about the city the institution is in?
- What would make you choose this institution over other programs?

### Previous Research

- Please list the different research experiences you have had.
- How many total years of research experience do you have?
- How has your research experience prepared you for graduate school?
- What questions did your research help answer?
- What was your role in developing research ideas?
- How did you manage your research project?
- What was innovative about your research?
- What was your favorite technique that you used in your undergraduate research?
- What was the biggest challenge you encountered in your undergraduate research, and how did you deal with it?
- How is your work distinct from your supervisor’s/principal investigator’s?
- What do you think are your most significant research accomplishments?
- What do you consider to be your best paper/work and why?
- What has been the impact of your research?
- Do you expect to publish before starting graduate school?
- If you were starting your project again today, what would you do differently?

### Current/Future Research

- What are your research interests?
- What are the big picture questions you want to investigate?
- What are the biggest challenges/questions in your field of research?
- How do you plan to approach your questions?
- How do you see this work impacting the field?
- How does the work you propose follow on from what you are already doing?
- What skills do you want to develop at this institution?
- Do you plan to apply for additional funding?
- What funding opportunities are you aware of, or what would you like to apply for?
- How would you convince a funding body that they should fund your research?
- How would you fit with the existing activities in the department?
- If we gave you unlimited resources, what would you do with them?
- Who do would you expect to collaborate with in the institution?
	- Why do you want to collaborate with them?
- What is an interesting paper you have read lately?

### If you have a specific project in mind...

- What is the overall importance of this project?
- Can you see any of your research proposal failing?
- What will you do if your hypothesis is proved wrong?
- What resources will you need?
- What opportunities for multi-disciplinary work does your research offer?
- 
### Potential Advisors

- What do you want to work on in my lab?
- What interests you about my research?
- What do you know about my research?
- Who are you interested in working with?
- What techniques have you learned that you could use in my lab?


### Teaching

- Do you have any teaching experience?
- How do you feel about teaching?
- How do you feel about mentoring undergrads?
- How would you deal with any conflict/disagreement within the research group?
- Do you have an example of when you have had to deal with a disagreement?
- 
### Personal

- What do you do in your free time (not in the lab)?
- What motivates you?
- What drives you as a scientist?
- Who has influenced you the most?
- How do you work best – independently, or with a team, at home?
- How do your interests fit with the strengths and goals of the program?
- What do you expect to be challenging about graduate school? What are your plans for managing those challenges?
- Graduate school often involves a combination of intense days, long nights, and high expectations. What strategies will you use to manage this combination of demands?
- What are your strengths and weaknesses?
- Tell us about a time when things didn’t go the way you wanted. How did you handle it, and what did you learn from the experience?
- Tell us about your most successful or interesting research experience in a lab environment. Which of your qualities helped facilitate this success?
- Describe a time that you encountered a significant personal obstacle? How did you handle it?
- Is there any information pertinent to your application that you would like to add?
- In what ways, other than research and teaching could you contribute to this department?
- What are your long term career goals


### Questions for you to ask current grad students

- Does the environment feel more collaborative or competitive?
- What is the funding structure/guarantee for students?
- Is it an inclusive environment?
- Where do you (and students in general) live?
- What is the area around campus like?
- Do you think the stipend reflects the cost of living?
- Is the university helpful with finding housing?
- How easy/difficult was the process of joining a lab?
- Do most people join their first choice lab?
- How much time are you expected to spend in the lab?
- How would you describe your PI's advising style?
- How do you maintain a successful relationship with your advisor?
- How regularly/quickly does your advisor publish?
- What research are you working on?
- How quickly were you able to start your research?
- Is the project you're working on what you thought you'd be doing, or has the project you're working on gone in any unexpected directions?
- Who is on your committee and why?
- Would you choose this advisor if you were doing it over?
- Do you get to attend conferences?
- What do you think of the courses - useful content, well taught, relevant to your research/goals?
- How easy/hard is it to customize the program?
- What would you change about the program?
- What kind of schedule do you work?
- What do grad students do in their free time?
- Do most students have a good work/life balance?
- Do grad students in this program hang out with each other?
- Do you know many people in grad school who regret starting it?
- Do you know people who have left the graduate program?
- What kind of resources does the program offer (e.g. for mental health, career development, learning new skills, etc.)?
- Is there anything you wish you had taken into consideration when making your decision about where to attend?

### Questions for you to to ask potential PI’s

- I read your paper/book X. Can you tell me about your future research goals related to X? What are your current projects?
- What research projects do you have that would be looking for graduate students?
- What advice would you give to a student who wants to be successful in your program? Are there any specific pitfalls to be avoided?
- What are the expectations for a graduate student in your lab?
- Do students create their own projects or work on something already developed/in progress?
- How is your lab organized? Do you have a lab manager, or do other members of the lab take on this role?
- Do you have lab/group meetings, and what is the format of those meetings?
- How much collaboration is there within the lab?
- How much do your students publish?
- How often do you sent students to conferences?
- How long do students in your lab take to complete their degree?
- What do students from your lab typically do after graduation?
- What is the big picture/goal/focus/priority of the department?

### Questions for you to ask other interviewers

(like program or admissions directors)

- What are the responsibilities of grad students in this program?
- What is the workload/time commitment?
- Do grad students have to TA? How many terms do you TA?
- Are students generally collaborative or competitive?
- How big is the program?
- What's the biggest strength of the program?
- What professional development services are available?
- How/when are students paired with advisors?
- What does the program do if someone doesn't find a lab to join by the deadline?
- What percentage of students complete the degree? Pass quals?
- How would you compare this program to X and Y?
- Is there funding available for attending things like conferences or summer schools?
- What are the career outcomes for students in this program?


## Field Specific Things

### Clinical Psychology

- [Mitch Prinstein](http://mitch.web.unc.edu/info-for-phd-applicants/)'s collection of info for Clinical Psychology PHD applicants including:
    - [Mitch's Uncensored Advice for Applying to Graduate School in Clinical Psychology](http://mitch.web.unc.edu/files/2017/02/MitchGradSchoolAdvice.pdf) 
    - [Tips on Applying to Graduate School](http://mitch.web.unc.edu/files/2013/10/TipsForApplyingToGradSchool.pdf) by Sophie Choukas-Bradley
    - [Before You Apply](http://mitch.web.unc.edu/files/2013/10/BeforeYouApply.pdf) by Casey Calhoun
- [Craig Rodriguez-Seijas's](https://sites.lsa.umich.edu/splat-lab/) [FAQ](https://sites.lsa.umich.edu/splat-lab/faqs/)

- [American Psychological Association](https://www.apa.org/index)'s [List of APA-Accredited Programs](https://www.apa.org/ed/accreditation/programs/)


### Individual Differences (Personality, Intelligence, etc)

- [Bill Revelle](https://www.personality-project.org)'s [Website has a collection of info](https://www.personality-project.org/org.html#howtoapply) 

- [Bill Revelle](https://www.personality-project.org)'s List of [Graduate Departments of Psychology with Personality Programs](https://www.personality-project.org/org.html#gradpsych)


### Social Psychology

- [Social Psychology Network Ranked List](https://www.socialpsychology.org/gsocial.htm)
- [SPSP's Social and Personality Graduate Program Directory](http://spsp.org/resources/student/grad-directory)

### Quantitative Psychology

- [List of schools for quantitative psychology](https://en.wikipedia.org/wiki/List_of_schools_for_quantitative_psychology)
- [2022 Grad Programs in Quant Methods Descriptions](https://drive.google.com/file/d/1bZKlZOzz2gvvJbhAt1CmgLfzTthwUudR/view?usp=share_link)
- [Matrix Algebra Prep](ttps://docs.google.com/document/d/1zJppucbjjIw38PyGbdlVY457xJ2fJFgT/edit?usp=share_link&ouid=116013359694141653434&rtpof=true&sd=true)
	
## Bonus Stuff
 

### Funded Terminal Master's Programs (Incomplete List)

- [College of William and Mary](https://www.wm.edu/as/psych-sciences/gradprogram/financial-support/index.php)
- [Villanova University](https://www1.villanova.edu/villanova/artsci/psychology/AcademicPrograms/graduate/current/assistantships.html)
- [Wake Forest University](http://psychology.wfu.edu/graduate-program/graduate-financial-aid-2/)


## Subreddits
- [/r/Gradadmissions](https://www.reddit.com/r/gradadmissions/)
- [/r/GradSchool](https://www.reddit.com/r/GradSchool/)
- [/r/AskAcademia](https://www.reddit.com/r/AskAcademia)

## Grad Cafe

- [gradcafe admission results](https://www.thegradcafe.com/survey/index.php)
- [Data Visualization of Timelines](https://www.reddit.com/r/gradadmissions/comments/7srxxy/decision_timelines_for_particular_universities/)
